Analysis Descriptives

### 2024-01-30 procesamiento/03-prod_analysis-descriptives.Rmd
up

```{r redist-index}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg,likert)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,prefineq,
                        class3=class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,country3,region,
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  na.omit()

@@

dfreg$redist <- factor(dfreg$redist,levels = 1:5,labels = labels)
set_label(dfreg$redist) <- "(b) It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes."

dfreg$prefineq <- factor(dfreg$prefineq,levels = 1:5,labels = labels)
set_label(dfreg$prefineq) <- "(a) For a society to be fair, differences in people’s standard of living should be small."

@@

as.data.frame(dfreg) %>%
  dplyr::select(prefineq, redist) %>%
  setNames(get_label(.)) %>%
  likert() %>%
plot(
  low.color = "#D30132",
  high.color = '#5586B4',
  center = 3,
  wrap = 30,
  # plot.percents = TRUE,
  text.size = 3
) +
  labs(title = "Redistributive preferences",caption = "r = 0.61")

ggsave(plot = last_plot(),filename = "redist_index.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 0.75,units = "cm",scale = 18)

@@

@@

```{r redist-homclass-class-country}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal2,redist,
                        class3=class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,country3,region,
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  na.omit()

@@

df_plot %>% 
ggplot()+
  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=class3,color=class3)) +
  geom_hline(yintercept = 68.81757,linetype=2)+ 
  geom_point(aes(x = reorder(country3, egal2_c),y = egal2_c),alpha=1,shape=4) +
  scale_shape_manual(values = c(6, 15, 16)) +
  scale_color_manual(values = c("blue", "#E7B800", "red")) +
  labs(title = "Redistributive preferences (index) and social class by country",x=NULL,y="Redistributive Preferences") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x=element_text(angle=45,hjust = 1),
        legend.title = element_blank())

@@

df_plot %>% 
ggplot()+
  geom_point(aes(x = reorder(country3, homclass_c),y = homclass,shape=class3,color=class3)) +
  geom_hline(yintercept = 0.3910297,linetype=2)+ 
  geom_point(aes(x = reorder(country3, homclass_c),y = homclass_c),alpha=1,shape=4) +
  scale_shape_manual(values = c(6, 15, 16)) +
  scale_color_manual(values = c("blue", "#E7B800", "red")) +
  labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Class-based network homogeneity ") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x=element_text(angle=45,hjust = 1),
        legend.title = element_blank())

>>>>

```{r redist-index}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg,likert)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,prefineq,
  class3,
  homclass,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp",
  "gini_mkt",
  d10d1,
  rgdpna,
  oecd,
  country2, country
) %>%
  mutate(logrgdpna = log(rgdpna),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") %>%
  na.omit()

@@

# polycor::hetcor(data = dfreg$redist,dfreg$prefineq)

dfreg$redist <- factor(dfreg$redist,levels = 1:5,labels = labels)
set_label(dfreg$redist) <- "(B) It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes."

dfreg$prefineq <- factor(dfreg$prefineq,levels = 1:5,labels = labels)
set_label(dfreg$prefineq) <- "(A) For a society to be fair, differences in people’s standard of living should be small."

@@

as.data.frame(dfreg) %>%
  dplyr::select(prefineq, redist) %>%
  setNames(get_label(.)) %>%
  likert() %>%
plot(
  low.color = "#D30132",
  high.color = '#5586B4',
  center = 3,
  wrap = 50,
  # plot.percents = TRUE,
  text.size = 3,
) +
  labs(title = "Redistributive preferences",caption = "r = 0.61")

ggsave(plot = last_plot(),filename = "redist_index.png",device = "png",
       path = here::here("output/images"),width = 1.7,height = 0.55,units = "cm",scale = 18)

@@

```{r n-ties}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$idunique <- 1:dim(df1)[[1]]

dfreg <- df1 %>% dplyr::select(idunique,egal2,
  class3,
  homclass,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp",
  "gini_mkt",
  d10d1,
  rgdpna,
  oecd,
  country2, country, country3,region,
) %>%
  mutate(logrgdpna = log(rgdpna),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") %>%
  na.omit() %>% 
  left_join(df1[,c("idunique","n_high","n_middle","n_low")])

phig<- sjPlot::plot_frq(data = dfreg$n_high,show.prc = F,show.n = F)
pmid<- sjPlot::plot_frq(data = dfreg$n_middle,show.prc = F,show.n = F)
plow<- sjPlot::plot_frq(data = dfreg$n_low,show.prc = F,show.n = F)

cowplot::plot_grid(phig, pmid, plow, labels = NULL, nrow = 3,ncol = 1)

ggsave(plot = last_plot(),filename = "n_status_class.png",device = "png",
       path = here::here("output/images"),width = 0.5,height = 1,units = "cm",scale = 20)
```

@@

```{r redist-homclass-class-country}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$idunique <- 1:dim(df1)[[1]]

dfreg <- df1 %>% dplyr::select(idunique,egal2,
  class3,
  homclass,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp",
  "gini_mkt",
  d10d1,
  rgdpna,
  oecd,
  country2, country, country3,region,
) %>%
  mutate(logrgdpna = log(rgdpna),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") %>%
  na.omit()

df1[,c("n_high","n_middle","n_low")]

@@

df_plot %>% 
ggplot()+
  geom_point(aes(x = reorder(country3, egal2_c),y = egal2,shape=class3,color=class3)) +
  geom_hline(yintercept = 68.81757,linetype=2)+ 
  geom_point(aes(x = reorder(country3, egal2_c),y = egal2_c),alpha=1,shape=4) +
  scale_shape_manual(values = c(6, 15, 16)) +
  scale_color_manual(values = c("blue", "#E7B800", "red")) +
  labs(title = "Redistributive preferences and social class by country",x=NULL,y="Redistributive Preferences") +
  theme(legend.position = "bottom",
        axis.text.x=element_text(angle=45,hjust = 1),
        legend.title = element_blank())

@@

df_plot %>% 
ggplot()+
  geom_point(aes(x = reorder(country3, homclass_c),y = homclass,shape=class3,color=class3)) +
  geom_hline(yintercept = 0.3910297,linetype=2)+ 
  geom_point(aes(x = reorder(country3, homclass_c),y = homclass_c),alpha=1,shape=4) +
  scale_shape_manual(values = c(6, 15, 16)) +
  scale_color_manual(values = c("blue", "#E7B800", "red")) +
  labs(title = "Class-based network homogeneity and social class by country",x=NULL,y="Class-based network homogeneity ") +
  theme(legend.position = "bottom",
        axis.text.x=element_text(angle=45,hjust = 1),
        legend.title = element_blank())
